The Linux Programming Interfaces

### 2018-09-26 CS/TLPI.tex
9.26

\subsection{Signals}
Signals are often described as ``software interrupts''
\subsection{Threads}

>>>>

\subsection{Signals}
Signals are often described as ``software interrupts''
\subsection{Threads}
Threads \textbf{share}
\begin{itemize}
\item Text(for program codes).
\item Data.
\item Heap.
\item virtual memory.
\item global variables.(for communication)
\end{itemize}
Threads \textbf{differ in}
\begin{itemize}
\item Stack.
\item local variables.
\item function call linkage information(why?).
\end{itemize}
Threads' \textbf{advantages}
\begin{itemize}
\item easy to share data rather than multiprocesses.
\item good for parallel processing
\end{itemize}

\subsection{Process Groups and Shell Job Control}
\subsection{Sessions, Controlling Terminals, and Controlling Processes}
\subsection{Pseudoterminals}
A pseudoterminal is a \textbf{pair of connected virtual devices} known as \textbf{master and slave}.\\
Master drives the user program and slave drives terminal-oriented program. This connection is like a bridge. e.g. \textit{telnet and ssh}.
\subsection{Date and Time}
\begin{itemize}
\item \textit{Realtime}.
\item \textit{Process time}.
\end{itemize}

\subsection{Client-Server Architecture}
\subsection{Realtime}
\href{https://www.cl.cam.ac.uk/~mgk25/linux-posix.1b.txt}{POSIX.1b}:
\subsection{The /proc File System}
A virtual file system that provide an \textbf{interface to kernel data structures}.

\section{System Programming Concepts}

\subsection{System Calls}
\book{87}
\subsection{Library Functions}
\subsection{The standard C Library; The GNU C Library(glibc)}
\subsection{Handling Errors from System Calls and Library Functions}

\subsection{Notes on the Example Programs in this book}

\subsubsection{Command-Line Options and Arguments}
\subsubsection{Common Functions and Header Files}
\book{95}

\subsection{Portability Issues}
